\vspace{-5mm}Equation-free analysis of a dynamically evolving multigraph

### 2016-02-02 report/multigraph_manuscript.tex
Added rho-kappa-embeddings to manuscript

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.9\textwidth]{multigraph-dmaps-3d}
  \caption{Figure showing embedding of two trajectories on different timescales. Initially they are separate, but eventually they're embedded in the same region as they evolve to the same coarse stationary state. \label{fig:dmaps-results}}
\end{figure}

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.75\textwidth]{placeholder}
  \caption{Embedding of steady states in $\rho$ / $\kappa$ plane, showing that DMAPS uncovered the coarse variables known from Bal\'{a}zs' paper}
  \label{fig:label}
\end{figure}

>>>>

\begin{figure}[h!]
  \vspace{-5mm}
  \centering
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[width=0.9\textwidth]{dmaps-3d-convergence}
    \subcaption{Figure showing embedding of two trajectories on
      different timescales. Initially they are separate, but
      eventually they're embedded in the same region as they evolve to
      the same coarse stationary state. Initial and final states are
      circled, and point size grows as more steps are
      taken in each trajectory. \label{fig:dmaps-results-regular}}
  \end{subfigure} \\ %%
  \begin{subfigure}{0.75\textwidth}
    \centering
    \includegraphics[height=3in]{dmaps-3d-convergence-zoom}
    \subcaption{An enlarged view of the final points in the previous
      plot, revealing the approach to a similar final
      state. \label{fig:dmaps-results-zoom}}
  \end{subfigure}%
  \caption{One dimensional embedding of different trajectories with DMAPS. \label{fig:dmaps-results}}
\end{figure}

\begin{figure}[ht!]
  % TODO
  \centering
  \includegraphics[width=0.75\textwidth]{dmaps-2d-rho-kappa}
  \caption{Embedding of steady states in $\rho$ / $\kappa$ plane,
    showing that DMAPS uncovered the coarse variables known from
    Bal\'{a}zs' paper \label{fig:dmaps-rk}}
\end{figure}
